---
title: "feedback"
author: "TMM"
format: html
---
Here is the conference feedback questionnaire rewritten as an interactive R Markdown:

```{r setup, include=FALSE}
library(shiny)
```

# 2023MSC Conference Feedback

Thank you for attending the 2023 Multi-Specialty Conference (2023MSC). We appreciate your feedback to improve future conferences.

```{r questions, echo=FALSE}
radioButtons("role", "I attended as a:", 
             choices = c("Speaker", "Attendee"),
             selected = NULL)

textInput("liked", "1. What did you like most about the conference?", "")

textInput("improve", "2. What could we have done better?", "")

radioButtons("attend", "3. Would you attend another conference organized by us in the future?",
             choices = c("Yes", "No"), 
             selected = NULL)

textInput("comments", "4. Do you have any other comments or suggestions?", "")
```

Thank you for your participation and feedback!

```{r submit, echo=FALSE} 
submitButton("Submit Responses")
```

This allows participants to select their role, answer text questions, choose radio button options, and submit the form interactively. The responses can be collected and analyzed in R.

Let me know if you would like any changes or have any questions!

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
