---
title: "2023 COLLABORATING FOR BETTER HEALTH:"
format: html
---

<img src="TMM_logo.svg" style="position: absolute; top: 0; right: 0; width: 5cm; height: 5cm;">

### A MULTI-SPECIALTY CONFERENCE ###

Welcome to the 2023 MSC website <p id="date"></p>

We provide information about the upcoming conference on **Collaborating for Better Health: A Multi-Specialty Conference <a href="https://m.facebook.com/story.php?story_fbid=pfbid0GW6vxSWAnPsC8nnvBzZjmRswTJdKEpDSM77wYmjNFaZKJfB1XQem2JNqNnWN3AhWl&id=100094220689116&mibextid=qC1gEa">#2023MSC</a>**. This conference is a joint initiative of **Taipei Municipal Wanfang Hospital** and **Hargeisa Group Hospital**, and aims to promote knowledge exchange and collaboration among health professionals from different specialties and regions.

The conference will be held on **August 13-14, 2023**, from 9:00 AM to 12:00 PM, at the Conference Hall of **Carro Edeg Hotel** in Hargeisa, Somaliland.



1) To **register** for the conference, please click <a href="https://shorturl.at/bpsvy">here</a>.

2) If you are also a speaker at the conference, please also submit your **CV and abstract** to the Conference Secretariat by email: texchi2@gmail.com


Current Statistics for Registered Participants:
<img src="<URL or file path of your PNG image>" alt="Description of image">

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

```{r, message=FALSE, echo=FALSE}

# Install and load necessary libraries; for presenting a pie chart of a statistics of conference registration
#install.packages("googlesheets4")
#install.packages("tidyverse")
#library(googlesheets4)
library(tidyverse)
library(dplyr)

## Read data from Google Sheet
#msc2023_participants <- read_sheet("https://docs.google.com/spreadsheets/d/16w-_RyZ7PgLvNTTeujzUJ7R-okNa30GmQfXK9omp8OI/edit")

# Read data from CSV file
msc2023_participants <- read.csv("2023MSC_form_Registration (Responses) - Form Responses 1.csv")


# Count the number of occurrences of each specialty
data_count <- msc2023_participants %>% count(`Specialty.in.Medicine`)

# Create pie chart with percentage labels and counts
ggplot(data_count, aes(x="", y=n, fill=`Specialty.in.Medicine`)) +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start=0) +
  theme_void() +
  ggtitle("Specialty in Medicine") +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name="Specialty") +
  geom_text(aes(label=paste0(round(n/sum(n)*100), "% (", n, ")")), position=position_stack(vjust=0.5))
  
# Create pie chart using ggplot2 from msc2023_participants dataset directly
#ggplot(msc2023_participants, aes(x="", y=<column containing values>, fill="Specialty in Medicine")) +
#  geom_bar(width = 1, stat = "identity") +
#  coord_polar("y", start=0) +
#  theme_void()



```


3) Program at a Glance: 
(<a href="TMM_SLN_tikzposter_2023August_portrait_agenda__TMM_Conference_.pdf" target="_blank" rel="noopener noreferrer" class="button"> Download Agenda
</a>)




<embed 
  type="application/pdf" 
  src="TMM_SLN_tikzposter_2023August_portrait_agenda__TMM_Conference_.pdf"
  width="100%" 
  height="1000px"
  zoom="130%"
>





TAIPEI MUNICIPAL WANFANG HOSPITAL VERSUS HARGEISA GROUP HOSPITAL

ON AUGUST 13-14, 2023, AT 09:00 AM, SUNDAY-MONDAY

VENUE: CONFERENCE HALL OF CARRO EDEG HOTEL, HARGEISA


**Conference <a href="handbook.html">Handbook</a> of 2023MSC**
  
This website is Updated on 31 July, 2023
(Powered by github)

<script>
document.getElementById("date").innerHTML = Date();
</script>

